---
title: 'Data Science - Homework #5'
author: "Jon Brock - JPB2210"
output: 
    github_document:
        toc: TRUE
        toc_depth: 2
---

```{r load packages, message = FALSE}
library(tidyverse)
```

***

***Note: I'm having a real tough time in life right now, so this is the best I could do given the circumstances. I'm changing my registration for this course to pass/fail.***  

## Problem #1
###### (*20 points*)
##### *Writing a function*

```{r initial code input}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Let's take a quick look at our data frame before we replace our `NA` values.

```{r data frame printing (pre)}
iris_with_missing
```

Now, let's write a function to replace `NA` values of numeric vectors to be the mean value of that vector, and `"virginica"` for character vectors.  

```{r writing functions}
replace_function <- function(x) {
    
    if (is.numeric(x)) {
        
        replace_na(x, mean(x, na.rm = TRUE))
        
    }
    
    else if (is.character(x)) {
        
        replace_na(x, "virginica")

    }
    
}

iris_with_missing <- map_df(iris_with_missing, replace_function)
```

Now, let's take another quick look at our data frame post-`NA` replacement.

```{r data frame printing (post)}
iris_with_missing
```

***

## Problem #2
###### (*25 points*)
##### *Tidy and plot longitudinal data*

```{r iteration of reading csv files, message = FALSE, warning = FALSE}
csv_files <- list.files("./data", pattern = "*.csv", full.names = TRUE) %>%  
    set_names(nm = basename(.)) %>% 
    map_df(read_csv, col_names = TRUE, col_types = cols(), .id = "filename") %>% 
    mutate(
        arm = str_sub(filename, 1,3),
        id = str_sub(filename, 5,6)) %>% 
    select(arm, id, week_1:week_8) %>% 
    mutate(arm = case_when(
        arm == "con" ~ "control_participant",
        arm == "exp" ~ "experimental_participant")) %>% 
    unite(participant, c(arm, id), remove = TRUE) %>% 
    pivot_longer(-participant, names_to = "week_no", values_to = "count")

csv_files
```

```{r ggplot of longitudinal data, fig.width = 8, fig.height = 6, dpi = 200, fig.align = 'center'}
csv_files %>% 
    ggplot(aes(x = week_no, y = count, group = participant, color = participant)) +
    geom_line() +
    labs(
        title = "Count metrics for control and experimental arms",
        subtitle = "[over the course of an eight week observation period]",
        x = "Week No.",
        y = "Count")
```

We observe that those in the experimental drug group have higher numeric values than those in the control group. For this homewor problem we do not know what these values represent, so we could say either the experimental drug improves one's condition (if higher values = better) or the experimental drug is harmful (if higher values = worse).

***

## Problem #3
###### (*35 points*)
##### *Create and plot simulations*

```{r simulation 1}
set.seed(1)

sim_regression = function(n, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, sqrt(50))
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
    )
  
  broom::tidy(ls_fit)
}
```

```{r simulation 2}
sim_results <-
    rerun(10000, sim_regression(n = 30)) %>% 
    bind_rows() %>% 
    filter(term == "x") %>% 
    select(-c(term, std.error, statistic)) %>% 
    mutate(reject_h0 =
               case_when(
                    p.value < 0.05 ~ "yes",
                    p.value >= 0.05 ~ "no"))
```

***

## Homework Resources  

*Given the enormous headache of trying to figure out this homework, I relied much more heavily on online resources than previous homeworks. I felt it necessary to cite all of my resources. They are listed below.*  

[https://www.gerkelab.com/blog/2018/09/import-directory-csv-purrr-readr/]()  
[https://serialmentor.com/blog/2016/6/13/reading-and-combining-many-tidy-data-files-in-R]()  
[https://www.hvitfeldt.me/blog/purrr-tips-and-tricks/#sources]()  
[https://github.com/STAT545-UBC/Discussion/issues/398]()  
[https://gist.github.com/ColinFay/d74d331825868b181860212cd1577b69]()  
[https://lsru.github.io/tv_course/TD_purrr_solution.html]()  
[https://github.com/DanOvando/learn-purrr]()  
[https://stats.idre.ucla.edu/r/faq/how-can-i-visualize-longitudinal-data-in-ggplot2/]()  
[https://community.rstudio.com/t/using-case-when-over-multiple-columns/17206]()  
[https://www.imachordata.com/linear-model-power-analysis-with-dplyr/]()  