---
title: 'Data Science - Homework #5'
author: "Jon Brock - JPB2210"
output: 
    github_document:
        toc: TRUE
        toc_depth: 2
---

```{r load packages, message = FALSE}
library(tidyverse)
```

***

## Problem #1
###### (*20 points*)
##### *Writing a function*

```{r initial code input}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

The following code prints out the existing values of the `Species` variable within the `iris_with_missing` data frame. This is for illustrative purposes.  

```{r demo of pre-function cleaning}
pull(iris_with_missing, Species)
```

We can now write a function that will replace all of the `NA`s in the `Species` variable with `"virginica"`.  

```{r writing functions, eval=FALSE}
species_replace <- function(x, y) {
    
    pull(x, y) %>% replace_na("virginica")

}

#################

is_list(iris_with_missing)
map(iris_with_missing, is_character)

iris_with_missing %>% 
    modify_if(is_character, replace_na("virginica")) %>% 
    str()

species_replace2 <- function(x) {
    
    if (is.character(x)) { 
        replace_na("virginica")
    }
    
    if (is.double(x){ 
        
        replace_na(mean())
    })
}




#from video online
    test_vector <- mean(pull(iris_with_missing$Sepal.Length, na.rm = TRUE))

test_function <- function(x,y){ 
    
    if is_character(x$y)
        
        replace_na(x$y, "virginica")
}
```

We can now use our new function `species_replace` to populate all of the `NA` values contained within the `Species` variable with `"virginica"`. We see from the following output that our function worked as it should.  

```{r demo of function and post-function cleaning, eval=FALSE}
species_replace(iris_with_missing, "Species")
```

***

## Problem #2
###### (*25 points*)
##### *Tidy and plot longitudinal data*

```{r iteration of reading csv files, message = FALSE, warning = FALSE}
csv_files <- list.files("./data", pattern = "*.csv", full.names = TRUE) %>%  
    set_names(nm = basename(.)) %>% 
    map_df(read_csv, col_names = TRUE, col_types = cols(), .id = "filename") %>% 
    mutate(
        arm = str_sub(filename, 1,3),
        id = str_sub(filename, 5,6)) %>% 
    select(arm, id, week_1:week_8) %>% 
    mutate(arm = case_when(
        arm == "con" ~ "control_participant",
        arm == "exp" ~ "experimental_participant")) %>% 
    unite(participant, c(arm, id), remove = TRUE) %>% 
    pivot_longer(-participant, names_to = "week_no", values_to = "count")

csv_files
```

```{r ggplot of longitudinal data, fig.width = 8, fig.height = 6, dpi = 200, fig.align = 'center'}
csv_files %>% 
    ggplot(aes(x = week_no, y = count, group = participant, color = participant)) +
    geom_line() +
    labs(
        title = "Count metrics for control and experimental arms",
        subtitle = "[over the course of an eight week observation period]",
        x = "Week No.",
        y = "Count")
```

We observe that those in the experimental drug group have higher numeric values 

***

## Problem #3
###### (*35 points*)
##### *Create and plot simulations*

```{r simulation}
set.seed(1)

sim_regression = function(n, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, sqrt(50))
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
    )
  
  broom::tidy(ls_fit)
}
```

```{r eval = FALSE}
output <- vector("list", length = 10000)

for (i in 1:10000) {
    
    output[[i]] = sim_regression(n = 30, beta1 = 1)
    output[[i]] = sim_regression(n = 30, beta1 = 2)
    output[[i]] = sim_regression(n = 30, beta1 = 3)
    output[[i]] = sim_regression(n = 30, beta1 = 4)
    output[[i]] = sim_regression(n = 30, beta1 = 5)
    output[[i]] = sim_regression(n = 30, beta1 = 6)
    
}

bind_rows(output)




#same code as above, but written using purrr language

output2 <-
    rerun(10000, sim_regression(n = 30)) %>% 
    bind_rows()

output2 %>% 
    filter(term == "x") %>% 
    select(-c(term, std.error, statistic)) %>% 
    mutate(reject_h0 = case_when(
                            p.value < 0.05 ~ "yes",
                            p.value >= 0.05 ~ "no")) %>% 
    count(reject_h0)


```


***

## Homework Resources  

*Given the enormous headache of trying to figure out this homework, I relied much more heavily on online resources than previous homeworks. I felt it necessary to cite all of my resources. They are listed below.*  

[https://www.gerkelab.com/blog/2018/09/import-directory-csv-purrr-readr/]()  
[https://serialmentor.com/blog/2016/6/13/reading-and-combining-many-tidy-data-files-in-R]()  
[https://www.hvitfeldt.me/blog/purrr-tips-and-tricks/#sources]()  
[https://github.com/STAT545-UBC/Discussion/issues/398]()  
[https://gist.github.com/ColinFay/d74d331825868b181860212cd1577b69]()  
[https://lsru.github.io/tv_course/TD_purrr_solution.html]()  
[https://github.com/DanOvando/learn-purrr]()  
[https://stats.idre.ucla.edu/r/faq/how-can-i-visualize-longitudinal-data-in-ggplot2/]()  
[https://community.rstudio.com/t/using-case-when-over-multiple-columns/17206]()  
[https://www.imachordata.com/linear-model-power-analysis-with-dplyr/]()  